The Impact of Loadshedding on SWIX sectors using DCC-GARCH models

### 2023-01-23 Paper/Paper.Rmd
Update 23 Jan

---
title: "The Impact of Loadshedding on SWIX sectors using DCC-GARCH models"
documentclass: "elsarticle"
Thesis_FP: FALSE
output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
  html_document:
    df_print: paged

@@

pacman::p_load(modelsummary, gt, knitr, kableExtra, tidyverse, lubridate, tinytex, rmarkdown, crypto2, quantmod, MTS, rmgarch, rugarch, tbl2xts, fmxdat, ggthemes, summarytools, vars, tseries, pander, cowplot, qpcR)

@@

@@

```{r Figure1,  warning =  FALSE, fig.align = 'center', fig.cap = "Caption Here \\label{Figure1}", fig.ext = 'png', fig.height = 3, fig.width = 6}

@@

```{r Figure2, warning =  FALSE, fig.align = 'center', fig.cap = "Caption Here \\label{Figure2}", fig.height = 3, fig.width = 6, dev = 'png'}

@@

# Splitting a page

>>>>

---
title: "The Impact of Loadshedding on SWIX sectors using DCC-GARCH models"
documentclass: "elsarticle"
Thesis_FP: FALSE
output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5

@@

pacman::p_load(modelsummary, gt, knitr, kableExtra, tidyverse, lubridate, tinytex, rmarkdown, crypto2, quantmod, MTS, rmgarch, rugarch, tbl2xts, fmxdat, ggthemes, summarytools, vars, tseries, pander, cowplot, qpcR, tidyquant, stargazer, data.table)

@@

```{r include=FALSE}
T40 <- read_rds("../data/T40.rds")

sectors <- T40 %>% pull(Sector) %>% unique()
sector_return <- list()
for(i in 1:length(sectors)){
    # Loop through sectors and calculate returns and cumulative returns
    sector_return[[i]] <- portfolio_return_function(T40, sector = sectors[i]) %>% group_by(Portfolio) %>% 
      mutate(cumreturn_Rand = (cumprod(1 + Returns))) %>% # Start at 1
      mutate(cumreturn_Rand = cumreturn_Rand/dplyr:::first(cumreturn_Rand)) %>% 
      mutate(Sector = sectors[i])
}
# Rename tibbles
names(sector_return) <- sectors
# Combine Dataframes
sectors_cum_return <- rbind(sector_return[[1]], sector_return[[2]], sector_return[[3]]) %>% arrange(date)
```

@@

```{r CumRet,  warning =  FALSE, fig.align = 'center', fig.cap = "Cumulative Returns per Sector for ALSI and SWIX \\label{CumRet}", fig.ext = 'png', fig.height = 3, fig.width = 6}

sectors_cum_return_plot <- sectors_cum_return %>% 
    ggplot() +
    geom_line(aes(date, cumreturn_Rand, colour = Portfolio), alpha = 0.8) + facet_wrap(~Sector) + fmxdat::fmx_cols() + 
    labs(y = "Cumulative Returns", x = "") + 
    fmxdat::theme_fmx(title.size = ggpts(25))
sectors_cum_return_plot

@@

```{r include=FALSE}
sectors_cum_return <- sectors_cum_return %>% filter(Portfolio == 'J400') # SWIX

swix_loadshed <- rbind(
sectors_cum_return %>% filter(date >= "2014-11-01" & date <= "2015-3-31"),
sectors_cum_return %>% filter(date >= "2019-02-01" & date <= "2019-3-31"),
sectors_cum_return %>% filter(date >= "2019-12-01" & date <= "2020-3-31"),
sectors_cum_return %>% filter(date >= "2021-3-01" & date <= "2021-6-30"),
sectors_cum_return %>% filter(date >= "2021-9-01" & date <= "2021-11-30"),
sectors_cum_return %>% filter(date >= "2022-2-01" & date <= "2022-4-30"),
sectors_cum_return %>% filter(date >= "2022-6-01" & date <= "2022-12-31"))

swix_no_loadshed <- sectors_cum_return %>% filter(!date %in% (swix_loadshed %>% pull(date)))

xts_swix_return <- sectors_cum_return %>% tbl_xts(., cols_to_xts = "Returns", spread_by = "Sector")

xts_swix_return_loadshed <- swix_loadshed %>% tbl_xts(., cols_to_xts = "Returns", spread_by = "Sector") 
xts_swix_return_no_loadshed <- swix_no_loadshed %>% tbl_xts(., cols_to_xts = "Returns", spread_by = "Sector")

fit.dcc = readRDS(file = "../fit.dcc.rds")
fit.dcc_ls = readRDS(file = "../fit.dcc_ls.rds")
fit.dcc_nls = readRDS(file = "../fit.dcc_nls.rds")

# Now we can use multf to estimate the dcc model using our
# dcc.spec:
fit.dcc = dccfit(spec.dcc, data = xts_swix_return, solver = "gosolnp", cluster = cl, fit.control = list(eval.se = TRUE), fit = multf)
fit.dcc_ls = dccfit(spec.dcc_ls, data = xts_swix_return_loadshed, solver = "gosolnp", cluster = cl, fit.control = list(eval.se = TRUE), fit = multf_ls)
fit.dcc_nls = dccfit(spec.dcc_nls, data = xts_swix_return_no_loadshed, solver = "gosolnp", cluster = cl, fit.control = list(eval.se = TRUE), fit = multf_nls)

# And that is our DCC fitted model!

# We can now test the model's fit as follows: Let's use the
# covariance matrices to test the adequacy of MV model in
# fitting mean residual processes:
RcovList <- rcov(fit.dcc)  # This is now a list of the monthly covariances of our DCC model series.
RcovList_ls <- rcov(fit.dcc_ls)
RcovList_nls <- rcov(fit.dcc_nls)

covmat = matrix(RcovList, nrow(xts_swix_return), ncol(xts_swix_return) * ncol(xts_swix_return), byrow = TRUE)
covmat_ls = matrix(RcovList, nrow(xts_swix_return_loadshed), ncol(xts_swix_return_loadshed) * ncol(xts_swix_return_loadshed), byrow = TRUE)
covmat_nls = matrix(RcovList, nrow(xts_swix_return_no_loadshed), ncol(xts_swix_return_no_loadshed) * ncol(xts_swix_return_no_loadshed), byrow = TRUE)

mc1 = MCHdiag(xts_swix_return, covmat)
mc1_ls = MCHdiag(xts_swix_return_loadshed, covmat_ls)
mc1_nls = MCHdiag(xts_swix_return_no_loadshed, covmat_nls)

dcc.time.var.cor <- rcor(fit.dcc)
dcc.time.var.cor_ls <- rcor(fit.dcc_ls)
dcc.time.var.cor_nls <- rcor(fit.dcc_nls)

dcc.time.var.cor <- aperm(dcc.time.var.cor, c(3, 2, 1))
dcc.time.var.cor_ls <- aperm(dcc.time.var.cor_ls, c(3, 2, 1))
dcc.time.var.cor_nls <- aperm(dcc.time.var.cor_nls, c(3, 2, 1))

dim(dcc.time.var.cor) <- c(nrow(dcc.time.var.cor), ncol(dcc.time.var.cor)^2)
dim(dcc.time.var.cor_ls) <- c(nrow(dcc.time.var.cor_ls), ncol(dcc.time.var.cor_ls)^2)
dim(dcc.time.var.cor_nls) <- c(nrow(dcc.time.var.cor_nls), ncol(dcc.time.var.cor_nls)^2)

dcc.time.var.cor <- renamingdcc(ReturnSeries = xts_swix_return, DCC.TV.Cor = dcc.time.var.cor)
dcc.time.var.cor_ls <- renamingdcc(ReturnSeries = xts_swix_return_loadshed, DCC.TV.Cor = dcc.time.var.cor_ls)
dcc.time.var.cor_nls <- renamingdcc(ReturnSeries = xts_swix_return_no_loadshed, DCC.TV.Cor = dcc.time.var.cor_nls)
```

```{r ALSI, warning =  FALSE, fig.align = 'center', fig.cap = "ALSI Weight Contribution \\label{ALSI}", fig.height = 3, fig.width = 6, dev = 'png'}
weights_plot(T40, "ALSI")
```

```{r SWIX, warning =  FALSE, fig.align = 'center', fig.cap = "SWIX Weight Contribution \\label{SWIX}", fig.height = 3, fig.width = 6, dev = 'png'}
weights_plot(T40, "SWIX")
```

```{r LogRet,  warning =  FALSE, fig.align = 'center', fig.cap = "Log Returns per Sector for the SWIX \\label{LogRet}", fig.ext = 'png', fig.height = 3, fig.width = 6}

log_returns_plot <- sectors_cum_return %>% mutate(Sector = factor(Sector, levels = c("Financials",  "Industrials", "Resources"))) %>% 
  ggplot() + geom_line(aes(x = date, y = Returns, colour = Sector, alpha = 1)) + 
facet_wrap(~Sector, scales = "free_y", nrow = 3) + 
guides(alpha = "none") + 
fmxdat::theme_fmx() +
labs(x = "", y = "", subtitle = " ") +
theme(legend.position = "none") +
scale_color_hue(l = 20) + 
scale_x_date(labels = scales::date_format("%Y"), date_breaks = "1 years") + 
theme(axis.text = element_text(size = 7))

log_returns_plot

@@

```{r, results = 'asis'}
star_fit.dcc <- fit.dcc@mfit$matcoef[rownames(fit.dcc@mfit$matcoef) %like% 'omega|alpha1|beta1|dcca1|dccb1',, drop = FALSE] #%>% data.frame()

# \\label{dccfitfull}

stargazer(star_fit.dcc,
          type = "text",
          title = "DCC GARCH Model Fit",
          ci = TRUE,
          ci.level = 0.95,
          p.auto = TRUE,
          star.cutoffs = c(0.05, 0.01, 0.001),
          align = TRUE)

```{r, results = 'asis' }
star_fit.dcc_ls <- fit.dcc_ls@mfit$matcoef[rownames(fit.dcc_ls@mfit$matcoef) %like% 'omega|alpha1|beta1|dcca1|dccb1',, drop = FALSE]

# \\label{dccfitls}

stargazer(star_fit.dcc_ls,
          type = "text",
          title = "Loadshedding DCC GARCH Model Fit",
          ci = TRUE,
          ci.level = 0.95,
          p.auto = TRUE,
          star.cutoffs = c(0.05, 0.01, 0.001),
          align = TRUE) 
```

```{r, results = 'asis'}
star_fit.dcc_nls <- fit.dcc_nls@mfit$matcoef[rownames(fit.dcc_nls@mfit$matcoef) %like% 'omega|alpha1|beta1|dcca1|dccb1',, drop = FALSE]

# \\label{dccfitnls}

stargazer(star_fit.dcc_nls,
          type = "text",
          title = "No Loadshedding DCC GARCH Model Fit",
          ci = TRUE,
          ci.level = 0.95,
          p.auto = TRUE,
          star.cutoffs = c(0.05, 0.01, 0.001),
          align = TRUE)
```

```{r DCCfullr,  warning =  FALSE, fig.align = 'center', fig.cap = "Dynamic Conditional Correlations: Resources \\label{DCCfullr}", fig.ext = 'png', fig.height = 3, fig.width = 6}

dcc.time.var.cor_r_plot <- ggplot(dcc.time.var.cor %>% filter(grepl("Resources_", Pairs), !grepl("_Resources", Pairs))) + 
  geom_line(aes(x = date, y = Rho, colour = Pairs)) + 
  theme_hc() + 
  #ggtitle("Dynamic Conditional Correlations: Resources") + 
  scale_x_date(labels = scales::date_format("%Y"), date_breaks = "1 years") + 
  annotate("text", 
           x = c(as.Date("2014-9-01"), as.Date("2018-12-01"), as.Date( "2019-10-01"), as.Date("2021-1-01"), as.Date("2022-02-01")), 
           y = -0.3, 
           label = c("Period 1", "Period 2", "Period 3", "Period 4", "Period 5"),
           angle = 90) +
  xlab("") +
  geom_rect(aes(xmin = as.Date("2014-11-01"), xmax = as.Date("2015-3-31"), ymin = -Inf, ymax = Inf), fill = "lightgray", alpha = 0.01)  +
  geom_rect(aes(xmin = as.Date("2019-02-01"), xmax = as.Date("2019-3-31"), ymin = -Inf, ymax = Inf), fill = "lightgray", alpha = 0.01) +
  geom_rect(aes(xmin = as.Date( "2019-12-01"), xmax = as.Date("2020-3-31"), ymin = -Inf, ymax = Inf), fill = "lightgray", alpha = 0.01) + 
  geom_rect(aes(xmin = as.Date("2021-3-01"), xmax = as.Date("2021-6-30"), ymin = -Inf, ymax = Inf), fill = "lightgray", alpha = 0.01) +
  geom_rect(aes(xmin = as.Date("2021-9-01"), xmax = as.Date("2021-11-30"), ymin = -Inf, ymax = Inf), fill = "lightgray", alpha = 0.01)

dcc.time.var.cor_r_plot

```{r DCCfullf,  warning =  FALSE, fig.align = 'center', fig.cap = "Dynamic Conditional Correlations: Financials \\label{DCCfullf}", fig.ext = 'png', fig.height = 3, fig.width = 6}

dcc.time.var.cor_f_plot <- ggplot(dcc.time.var.cor %>% filter(grepl("Financials_", Pairs), !grepl("_Financials", Pairs))) + 
  geom_line(aes(x = date, y = Rho, colour = Pairs)) + 
  theme_hc() + 
  ggtitle("Dynamic Conditional Correlations: Financials") +
  scale_x_date(labels = scales::date_format("%Y"), date_breaks = "1 years") + 
  annotate("text", 
           x = c(as.Date("2014-9-01"), as.Date("2018-12-01"), as.Date( "2019-10-01"), as.Date("2021-1-01"), as.Date("2022-02-01")), 
           y = -0.3, 
           label = c("Period 1", "Period 2", "Period 3", "Period 4", "Period 5"),
           angle = 90) +
  xlab("") +
  geom_rect(aes(xmin = as.Date("2014-11-01"), xmax = as.Date("2015-3-31"), ymin = -Inf, ymax = Inf), fill = "lightgray", alpha = 0.01)  +
  geom_rect(aes(xmin = as.Date("2019-02-01"), xmax = as.Date("2019-3-31"), ymin = -Inf, ymax = Inf), fill = "lightgray", alpha = 0.01) +
  geom_rect(aes(xmin = as.Date( "2019-12-01"), xmax = as.Date("2020-3-31"), ymin = -Inf, ymax = Inf), fill = "lightgray", alpha = 0.01) + 
  geom_rect(aes(xmin = as.Date("2021-3-01"), xmax = as.Date("2021-6-30"), ymin = -Inf, ymax = Inf), fill = "lightgray", alpha = 0.01) +
  geom_rect(aes(xmin = as.Date("2021-9-01"), xmax = as.Date("2021-11-30"), ymin = -Inf, ymax = Inf), fill = "lightgray", alpha = 0.01)

dcc.time.var.cor_f_plot

```{r DCCfulli,  warning =  FALSE, fig.align = 'center', fig.cap = "Dynamic Conditional Correlations: Industrials \\label{DCCfulli}", fig.ext = 'png', fig.height = 3, fig.width = 6}

dcc.time.var.cor_i_plot <- ggplot(dcc.time.var.cor %>% filter(grepl("Industrials_", Pairs), !grepl("_Industrials", Pairs))) + 
  geom_line(aes(x = date, y = Rho, colour = Pairs)) + 
  theme_hc() + 
  ggtitle("Dynamic Conditional Correlations: Industrials") +
  scale_x_date(labels = scales::date_format("%Y"), date_breaks = "1 years") + 
  annotate("text", 
           x = c(as.Date("2014-9-01"), as.Date("2018-12-01"), as.Date( "2019-10-01"), as.Date("2021-1-01"), as.Date("2022-02-01")), 
           y = -0.1, 
           label = c("Period 1", "Period 2", "Period 3", "Period 4", "Period 5"),
           angle = 90) +
  xlab("") +
  geom_rect(aes(xmin = as.Date("2014-11-01"), xmax = as.Date("2015-3-31"), ymin = -Inf, ymax = Inf), fill = "lightgray", alpha = 0.01)  +
  geom_rect(aes(xmin = as.Date("2019-02-01"), xmax = as.Date("2019-3-31"), ymin = -Inf, ymax = Inf), fill = "lightgray", alpha = 0.01) +
  geom_rect(aes(xmin = as.Date( "2019-12-01"), xmax = as.Date("2020-3-31"), ymin = -Inf, ymax = Inf), fill = "lightgray", alpha = 0.01) + 
  geom_rect(aes(xmin = as.Date("2021-3-01"), xmax = as.Date("2021-6-30"), ymin = -Inf, ymax = Inf), fill = "lightgray", alpha = 0.01) +
  geom_rect(aes(xmin = as.Date("2021-9-01"), xmax = as.Date("2021-11-30"), ymin = -Inf, ymax = Inf), fill = "lightgray", alpha = 0.01)

dcc.time.var.cor_i_plot

```{r include=FALSE}
dcc.time.var.cor_ls <- dcc.time.var.cor_ls %>% mutate(Period = case_when(date >= "2014-11-01" & date <= "2015-3-31" ~ "Period 1",
                              date >= "2019-02-01" & date <= "2019-3-31" ~ "Period 2",
                              date >= "2019-12-01" & date <= "2020-3-31" ~ "Period 3",
                              date >= "2021-3-01" & date <= "2021-6-30" ~ "Period 4",
                              date >= "2021-9-01" & date <= "2021-11-30" ~ "Period 5",
                              date >= "2022-2-01" & date <= "2022-4-30" ~ "Period 6"))
```

### 2023-01-23 Paper/Paper.tex
Update 23 Jan

\hypertarget{splitting-a-page}{%
\section{Splitting a page}\label{splitting-a-page}}

>>>>

\begin{figure}[H]

{\centering \includegraphics{Paper_files/figure-latex/CumRet-1}

}

\caption{Cumulative Returns per Sector for ALSI and SWIX \label{CumRet}}\label{fig:CumRet}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics{Paper_files/figure-latex/ALSI-1}

}

\caption{ALSI Weight Contribution \label{ALSI}}\label{fig:ALSI}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics{Paper_files/figure-latex/SWIX-1}

}

\caption{SWIX Weight Contribution \label{SWIX}}\label{fig:SWIX}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics{Paper_files/figure-latex/LogRet-1}

}

\caption{Log Returns per Sector for the SWIX \label{LogRet}}\label{fig:LogRet}
\end{figure}

\hypertarget{dcc-garch-model-fit}{%
\section{DCC GARCH Model Fit}\label{dcc-garch-model-fit}}

\hypertarget{estimate-std.-error-t-value-pr-t}{%
\subsection{Estimate Std. Error t value Pr(\textgreater{} \textbar{}
t\textbar{} )}\label{estimate-std.-error-t-value-pr-t}}

{[}Resources{]}.omega 0.00000 0.00001 0.304 0.761\\
{[}Resources{]}.alpha1 0.005 0.033 0.147 0.883\\
{[}Resources{]}.beta1 0.947 0.050 18.750 0\\
{[}Industrials{]}.omega 0.00000 0.00000 1.755 0.079\\
{[}Industrials{]}.alpha1 0.017 0.009 1.822 0.068\\
{[}Industrials{]}.beta1 0.907 0.017 54.781 0\\
{[}Financials{]}.omega 0.00000 0.00000 0.966 0.334\\
{[}Financials{]}.alpha1 0.032 0.022 1.492 0.136\\
{[}Financials{]}.beta1 0.907 0.033 27.601 0\\
{[}Joint{]}dcca1 0.039 0.005 7.807 0\\
{[}Joint{]}dccb1 0.949 0.008 123.286 0\\
------------------------------------------------------------

\hypertarget{loadshedding-dcc-garch-model-fit}{%
\section{Loadshedding DCC GARCH Model
Fit}\label{loadshedding-dcc-garch-model-fit}}

\hypertarget{estimate-std.-error-t-value-pr-t-1}{%
\subsection{Estimate Std. Error t value Pr(\textgreater{} \textbar{}
t\textbar{} )}\label{estimate-std.-error-t-value-pr-t-1}}

{[}Resources{]}.omega 0.00004 0.00003 1.399 0.162\\
{[}Resources{]}.alpha1 0.00000 0.101 0.00000 1.000\\
{[}Resources{]}.beta1 0.791 0.161 4.907 0.00000\\
{[}Industrials{]}.omega 0.00001 0.00000 24.162 0\\
{[}Industrials{]}.alpha1 0.00000 0.028 0.00000 1.000\\
{[}Industrials{]}.beta1 0.825 0.023 35.958 0\\
{[}Financials{]}.omega 0.00003 0.00001 3.121 0.002\\
{[}Financials{]}.alpha1 0.018 0.058 0.306 0.760\\
{[}Financials{]}.beta1 0.672 0.071 9.408 0\\
{[}Joint{]}dcca1 0.050 0.015 3.414 0.001\\
{[}Joint{]}dccb1 0.895 0.032 27.579 0\\
------------------------------------------------------------

\hypertarget{no-loadshedding-dcc-garch-model-fit}{%
\section{No Loadshedding DCC GARCH Model
Fit}\label{no-loadshedding-dcc-garch-model-fit}}

\hypertarget{estimate-std.-error-t-value-pr-t-2}{%
\subsection{Estimate Std. Error t value Pr(\textgreater{} \textbar{}
t\textbar{} )}\label{estimate-std.-error-t-value-pr-t-2}}

{[}Resources{]}.omega 0.00000 0.00000 0.437 0.662\\
{[}Resources{]}.alpha1 0.026 0.021 1.256 0.209\\
{[}Resources{]}.beta1 0.934 0.035 26.758 0\\
{[}Industrials{]}.omega 0.00000 0.00001 0.365 0.715\\
{[}Industrials{]}.alpha1 0.023 0.036 0.641 0.521\\
{[}Industrials{]}.beta1 0.912 0.074 12.253 0\\
{[}Financials{]}.omega 0.00000 0.00001 0.369 0.712\\
{[}Financials{]}.alpha1 0.039 0.051 0.771 0.441\\
{[}Financials{]}.beta1 0.908 0.075 12.101 0\\
{[}Joint{]}dcca1 0.036 0.005 6.747 0\\
{[}Joint{]}dccb1 0.954 0.008 120.623 0\\
------------------------------------------------------------

\begin{figure}[H]

{\centering \includegraphics{Paper_files/figure-latex/DCCfullr-1}

}

\caption{Dynamic Conditional Correlations: Resources \label{DCCfullr}}\label{fig:DCCfullr}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics{Paper_files/figure-latex/DCCfullf-1}

}

\caption{Dynamic Conditional Correlations: Financials \label{DCCfullf}}\label{fig:DCCfullf}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics{Paper_files/figure-latex/DCCfulli-1}

}

\caption{Dynamic Conditional Correlations: Industrials \label{DCCfulli}}\label{fig:DCCfulli}
\end{figure}
